\Large{Research Seminar Software Science} \\ \huge{Simulation of monadic effects in Haskell}

### 2018-05-05 paper.tex
added subsection parser combinators

>>>>

    \subsection{Parser Combinators}

    The three primitive parsers that were defined in the previous subsection aren't very helpful when used separately. Hence, these parsers have to be combined together through some operators in order to actually produce something useful. In this subsection, two operators are introduced: \textit{sequence} and \textit{alternation}.

    \subsubsection{Sequencing}

    \subsubsection{Alternation}
